\input{../../preamble}

\title{AI for Coding}

\author{John Stachurski}


\date{2025}


\begin{document}

\begin{frame}
  \titlepage
\end{frame}



\begin{frame}
    \frametitle{Topics}

    \begin{itemize}
        \item Foo
        \vspace{0.5em}
        \item Bar
        \vspace{0.5em}
    \end{itemize}

\end{frame}


\begin{frame}

    Choice of language and environment matters:

\end{frame}


\begin{frame}

    Claude Sonnet:
    
    ``I'm definitely stronger with Python than MATLAB.

    While I'm knowledgeable about both languages, my capabilities with Python
    are more comprehensive. I have deeper familiarity with Python's extensive
    ecosystem of libraries, frameworks, and modern development practices. I can
    more confidently help with advanced Python topics, debugging complex Python
    code, and implementing Python best practices.''

\end{frame}


\begin{frame}
    
    Claude Sonnet:

    ``I'm definitely stronger with Python than Julia.

    Python is one of my most proficient languages - I have deep familiarity with
    its syntax, libraries, frameworks, and best practices across many domains
    including data science, web development, machine learning, and
    general-purpose programming.

    While I understand Julia's syntax and core concepts, my expertise with it
    isn't as comprehensive as with Python.''

\end{frame}


\begin{frame}
    
    see \url{https://www.reddit.com/r/aipromptprogramming/s/awUqcBV4Jq}

    AI doesn't see the big picture It can ace small tasks but struggles to
    connect them meaningfully. You still need to be the architect.

    Context is fragile: AI forgets. A lot. I had to constantly remind it of
    previous decisions, or it would rewrite things back to how they were before.

    Debugging is mostly on you 

    Once things get weird, AI starts guessing

    Often, it’s faster to dive in and fix it manually than go back and forth. 

    To vibe code at 100\% efficiency, you still need solid coding skills because you’ll
    inevitably hit issues that require deeper understanding

    Sometimes AI gets really weird 

    Occasionally, the AI starts doing totally bizarre things

\end{frame}

\end{document}


